% David P. Adams - Curriculum Vitae
%
% Copyright (C) 2025 David P. Adams dpadams@fullerton.edu
%
% Adapted from http://jblevins.org/cv.tex

\documentclass[12pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry} 
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{sectsty}
\frenchspacing
\clubpenalty=500000
\widowpenalty=500000
% Set your name here
\def\name{David P. Adams}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {public policy, public administration, environmental policy, collaborative governance, American political institutions},
  pdftitle = {\name: David P. Adams - Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom font for improved readability
\usepackage{fontspec}
\setmainfont{Fira Sans}[
    UprightFont = *-Regular,
    BoldFont = *-Bold,
    ItalicFont = *-Italic,
    BoldItalicFont = *-BoldItalic
]


% Adjusting section and subsection styles for new font
\sectionfont{\sffamily\bfseries\Large}
\subsectionfont{\sffamily\bfseries\itshape\large}
\subsubsectionfont{\sffamily\bfseries\itshape\normalsize}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\begin{document}
    
% Place name at left
%{\huge \name}
    
% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}
\smallskip
\centerline{\small{\textsc{curriculum vitae}}}

\bigskip

% Contact Information
\noindent

\begin{minipage}[t]{0.55\textwidth}
    Division of Politics, Administration, and Justice \\
    California State University, Fullerton \\
    800 North State College Boulevard  \\
    Fullerton, California 92834
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth}
    Office: \hspace{6em}(657) 278-4770 \\
    Cell: \hspace{6.5em} (949) 659-3621 \\
    Website: \hspace{6.5em}\href{https://dadams.io}{dadams.io} \\
    Email: \hspace{1.2em}\href{mailto:dpadams@fullerton.edu}{dpadams@fullerton.edu}
\end{minipage}


  \section*{Education}

  \begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item Ph.D., Public Policy and Public Administration, Auburn University, May 2016. \vspace{0.2cm}
      % Received May 22, 2016
  \item M.P.A., Public Administration, Auburn University, May 2010. \vspace{0.2cm}
    % Received May 14, 2010
  \item B.S., Political Science and Government, Kennesaw State University, May 2008.
    % Received May 14, 2008
  \end{itemize}
  
  \section*{Academic and Professional Appointments}

  \begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
      \item Public Administration Coordinator and MPA Director, Division of Politics, Administration, and Justice, California State University, Fullerton, 2024--Present. \vspace{0.2cm}
      \item Associate Professor of Public Administration (with Tenure), Division of Politics, Administration, and Justice, California State University, Fullerton, 2022--Present. \vspace{0.2cm}
      \item Assistant Professor of Public Administration, Division of Politics, Administration, and Justice, California State University, Fullerton,  2016--2022.\vspace{0.2cm}
      \item Adjunct Professor, Department of Political Science, Auburn University, Summer 2016.
  \end{itemize}

\section*{Research}

\subsection*{Publications}

\subsubsection*{Peer-Reviewed Journal Articles}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt

    \item Adams, David P., Jonathan M. Fisk, and Adam F. Mayer. 2025. \href{https://doi.org/10.1080/10841806.2025.2537600}{``Administrative Resilience under Pressure: Environmental Governance and Institutional Adaptation.''} \emph{Administrative Theory \& Praxis}, 1--7.

    \item McKnight, Steve, Adams, David P., and Fisk, Jonathan M. 2025. \href{https://doi.org/10.1111/psj.70064}{``Does Disclosure Matter? Coupling Information to Performance in Texas.''} \emph{Policy Studies Journal}.

    \item Amin, Alisha, David P. Adams, Jonathan M. Fisk, and Adam F. Mayer. 2025. \href{https://doi.org/10.1080/1523908X.2025.2480289}{``Plugged In? Assessing the Distribution of Orphaned Wells.''} \emph{Journal of Environmental Policy and Planning}, March, 1--14.

    \item Mahfuza, Zachary, Jonathan Fisk, and David P. Adams. 2021. \href{https://doi.org/10.1111/polp.12401}{``Crude Contempt: Examining Local Pushback to Oil and Gas Development in California.''} \emph{Journal of Politics and Policy} 49(2).

    \item Adams, David P., Meriem Doucette, and Justin Tucker. 2019. \href{https://escholarship.org/uc/item/2mz2n6qk}{``Affluence, Risk, and Community Engagement: The Case of Ascon and Huntington Beach.''} \emph{California Journal of Politics and Policy} 11(3).   

\end{itemize}

\subsubsection*{Edited Textbooks}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Doucette, Meriem, and David P. Adams, eds. 2019. \emph{Ethics in Public Administration: Ethics, Corruption, and Public Policy}. San Diego, CA: Cognella.
\end{itemize}

\subsubsection*{Textbook Chapters}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Adams, David P. 2019. ``Minnesota Environmental Policy.'' In \emph{Minnesota Government and Politics}, edited by James B. Cottrill, Shawn E. Schooley, Steven C. Wagner, and Shoua S. Yang. Dubuque, IA: Great River Learning Publishers.
\end{itemize}

\subsection*{Books Under Contract}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Adams, David P., Jonathan M. Fisk, and John Morris. \emph{Navigating Water Quality Outcomes in American Watersheds}. Under Contract with Cambridge University Press: New York, N.Y.
\end{itemize}

\subsection*{Manuscripts Under Review}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  
    \item Nahar, Nurun, David P. Adams, Jonathan M. Fisk, Adam F. Mayer, and John C. Morris. ``Inspector-Level Bureaucracy: Drilling into Discretion in a State Natural Resource Agency.'' Under revision review at \emph{Review of Policy Research}.

    \item Adams, David P. ``The Code Is the Policy: Blockchain Governance and the Authoritarian Pursuit of Administrative Efficiency.'' Under review at \emph{Administrative Theory \& Praxis}.
    
    \item Arthur, Prince, David P. Adams, Jonathan M. Fisk, Matthew G. Jarvis, and Christopher A. Simon. ``Exploring the Role of Multi-Agency Coordination in California's Climate Investment Program 2015--2024.'' Under review at \emph{Public Organization Review}.

\end{itemize}

\subsection*{Manuscripts in Preparation}
  \begin{itemize} \leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    
    \item Amin, Alisha, David P. Adams, Jonathan M. Fisk, Binita Mahato, and Nurun Nahar. ``Linking Disclosure to Performance: Assessing Colorado's 2021 Spill Reporting Rule and Operator Performance.''
  \end{itemize}

\subsection*{Refereed Presentations}
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt

    \item Amin, Alisha, David P. Adams, Jonathan M. Fisk, Binita Mahato, and Nurun Nahar. 2025. ``Linking Disclosure to Performance: Assessing Colorado's 2021 Spill Reporting Rule and Operator Performance.'' Paper presented at the annual conference of the American Society for Public Administration, Washington, D.C.

    \item Authur, Prince, David P. Adams, Jonathan M. Fisk, Matthew G. Jarvis, and Christopher A. Simon. 2025. ``Pioneering Policy: Exploring the Role of Multi-Agency Collaboration in California's Climate Investment Program 2015--2024.'' Paper presented at the annual conference of the American Society for Public Administration, Washington, D.C.
    
    \item Adams, David P., Jonathan M. Fisk, and John C. Morris. 2024. ``Navigating Water Quality Outcomes in American Watersheds.'' Paper presented at the annual conference of the American Society for Public Administration, Minneapolis, MN.
    
    \item Adams, David P., Nurun Nahar, Jonathan M. Fisk, Adam F. Mayer, and John C. Morris. 2024. ``Inspector-Level Bureaucracy: Drilling into Discretion in a State Natural Resource Agency.'' Paper presented at the national conference of the American Society for Public Administration, Minneapolis, MN.
    
    \item Adams, David P., Jonathan M. Fisk, and Steve McKnight. 2024. ``Does Disclosure Matter? Coupling Information to Performance in Texas.'' Paper presented at the national conference of the American Society for Public Administration, Minneapolis, MN.
    
    \item Adams, David P., Alisha Amin, Jonathan M. Fisk, and Adam F. Mayer. 2024. ``Plugged In? Assessing the Distribution of Orphaned Wells.'' Paper presented at the annual conference of the Midwest Political Science Association, Chicago, IL.

    \item Adams, David P., Zachary Mahafza, Jonathan M. Fisk, and Hanna Krawczyk. 2021. ``Head for The Hills: An Environmental Justice Inquiry of Spills within Colorado's Oil and Gas Industry.'' Paper presented at the virtual national conference of the American Society for Public Administration.

    \item Herrera, Veronica, David P. Adams, and Lidia E. Nuño. 2020. ``American Indian Youth and Substance Use: Multilevel Analysis of School Related Factors.'' Paper presented as part of the special event ``Adolescence in the Context of Domestic and Global Diversity`` at the Society of Research on Adolescence (SRA) Biennial Meeting, San Diego, CA.
    
    \item Adams, David P. and John Shipman. 2019. ``Energy Efficiency Retrofits in Underserved Communities.'' Paper presented at the International Symposium on Society and Natural Resource Management, Oshkosh, WI.
    
    \item Adams, David P., Meriem Doucette, and Justin Tucker. 2018. ``Affluence, Risk, and Community Engagement: The Case of Ascon and Huntington Beach.'' Paper presented at the Midwest Political Science Association Annual Meeting, Chicago, IL.
    
    \item Adams, David P. 2015. ``Central Network Importance for Collaborative Environmental Management.'' Paper presented at the American Political Science Association Annual Meeting, San Francisco, CA.
    
    \item Adams, David P. 2015. ``Central Network Importance for Water Quality.'' Paper presented at the International Symposium on Society and Resource Management Annual Meeting, Charleston, SC.
    
    \item Adams, David P. 2014. ``Environmental Outcomes of Local Watershed Information Networks.'' Paper presented at the Midwest Political Science Association Annual Meeting, Chicago, IL.
    
    \item Bowling, Cynthia, Kisha Hardwick, and David P. Adams. 2014. ``Outstanding Programs and Potential Policy Diffusion Across the States.'' Paper presented at the Southern Political Science Association Annual Meeting, New Orleans, LA.
    
    \item Koehler, John, and David P. Adams. 2013. ``Broadband Connections and Voter Turnout.'' Paper presented at the Southern Political Science Association Annual Meeting, Orlando, FL.
    
    \item Hale, Kathleen, Mitchell Brown, and David P. Adams. 2012. ``Enhancing Graduate Student Learning through Course Coordination and Integrated Assignments.'' Paper presented at The Teaching and Learning Conference of the American Political Science Association Annual Meeting, Washington, D.C.
    
    \item Hale, Kathleen, Mitchell Brown, and David P. Adams. 2012. ``Enhancing Student Learning through Multi-Course Coordination and Learning Module Integration.'' Paper presented at the Southern Political Science Association Annual Meeting, New Orleans, LA.
    
    \item Adams, David P. 2010. ``Constructing and Combating an Environmental Problem: Nonpoint Source Pollution in the Wolf Bay Watershed.'' Poster presented at the Auburn University Department of Agriculture Economics and Rural Sociology Mobile Bay Watershed Project Annual Meeting, Auburn, AL.
  \end{itemize}
  

\section*{Dissertation}
    \begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
        \item \emph{Dissertation:} ``The Environmental Outcomes of Collaborative Natural Resource Institutions.'' 
        \item \emph{Committee:} Kathleen Hale (Chair), Mitchell Brown (Co-chair),
        Gerry Gryski, \\Linda Dennard, and Elise Irwin.
        \item \emph{Award:} Auburn University Graduate School's Distinguished Dissertation Award
    \end{itemize}
		
\section*{Teaching Experience}

\subsection*{California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item POSC 588: Collaborative Governance
  \item POSC 315: Politics and Policy Making in America
  \item POSC 320: Introduction to Public Administration
  \item POSC 509: Foundations of Public Administration
  \item POSC 521: Capstone: Public Administration Theory
\end{itemize}

\subsection*{Auburn University}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item State and Local Government
  \item Introduction to Public Administration
  \item Research Methods I
  \item Introduction to Political Theory
  \item American Government
  \item Policy Process
\end{itemize}

\section*{Grants, Honors, and Awards}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item California State University, Fullerton RSCA Intramural Grant, \$15,000, 2025--2026.
  \item California State University, Fullerton H\&SS Dean's Research Award for Associate Professors, \$2,500, Spring 2025.
  \item California State University, Fullerton Award for Outstanding Service, 2023.
  \item California State University, Fullerton Office of Research and Sponsored Projects Summer Grant, \$5,000, 2021.
  \item California State University, Fullerton Faculty Advisor of Distinction Award, 2018.
  \item Auburn University Graduate School Distinguished Dissertation Award, 2016.
  \item Auburn University Department of Political Science PhD Student of the Year Award, 2016.
  \item Auburn University College of Liberal Arts GTA Teaching Award, 2016.
  \item SPSA Prestage-Cook Travel Award, 2014.
  \item Omicron Delta Kappa Honor Society, 2013.
  \item Delta Epsilon Iota Honor Society, 2013.
  \item John and Elizabeth Morris Fund for Excellence Travel Grant, 2012.
  \item Auburn University College of Liberal Arts Dissertation Research and Travel Grant, 2012.
  \item Pi Sigma Alpha Honor Society, 2011.
  \item Golden Key International Honour Society, 2010.
  \item Best Performance Award for MPA Comprehensive Exam, 2010.
  \item Pi Alpha Alpha Honor Society, 2009.
\end{itemize}

\section*{Professional Development}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item NASPAA Accreditation Institute, 2017, 2024
  \item Data Analysis with Python Certification, FreeCodeCamp, 2021
  \item Interuniversity Consortium for Political and Social Research (ICPSR) Summer Program in Quantitative Methods of Social Research, University of Michigan, 2012
  \item Teaching and Learning Conference of the American Political Science Association, Washington, D.C., 2012
\end{itemize}

\section*{Service}

\subsubsection*{Service to the Public Administration Unit at California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item PA Coordinator and MPA Program Director, 2024--present
    \item MPA Program Faculty Advisor, 2024--2025
    \item Advisor, Public Administration Student Association (PASA), 2025--present
    \item Advisor, Pi Alpha Alpha International Honor Society, 2023--present
    \item MPA Program Admissions Coordinator, 2023--2025
    \item BAPA Program Faculty Advisor, 2023--2025
    \item Chair, PS/PA Diversity, Equity, and Inclusion Committee, 2023--present
    \item PA Program Curriculum and Assessment Committee, 2020--2022, 2024--present
    \item PA Program Faculty Search Committee, 2023--2024
    \item PA Program Awards Committee, 2018--present
    \item PA Program Assessment Coordinator, 2017--present
    \item MPA Program NASPAA Accreditation Liaison, 2017--present
\end{itemize}

\subsubsection*{Service to the Division of Politics, Administration, and Justice at California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Chair, Division Search Committee (Public Administration), 2025--present
    \item Chair, Division Personnel Committee, 2024--2025
    \item Member, Division Personnel Committee, 2023--2024
    \item Executive Committee, 2018--2022, 2023--present
    \item Advisor, Pi Sigma Alpha National Political Science Honor Society, 2023--2025
    \item Division Peer Review Committee, 2022--2023, 2024--2025
    \item Division Commencement Committee, 2017--2018, 2024--2025
    \item Division Awards Committee, 2018--2020, 2023--2024
    \item Division Curriculum Committee, 2020--2022
    \item Public Administration Faculty Search Committee, 2023--2024
\end{itemize}

\subsubsection*{Service to the College of Humanities and Social Sciences at California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item College Personnel Standards Review Committee (CPSRC), 2025--present
    \item Faculty Research and Grants Committee, 2023--2025
\end{itemize}

\subsubsection*{Service to the University at California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Library and Technology Committee, 2025--present
    \item Graduate Education Committee, 2025--present
    \item Assessment \& Educational Effectiveness Committee, 2024--2025
    \item Faculty Advisor, Tau Kappa Epsilon International Fraternity, 2017--2024
    \item Member, G.E. Assessment Faculty Learning Community, 2019--2021
    \item Faculty Advisor, United Nations Association--USA; Generation United Nations, 2017--2019
\end{itemize}

\subsubsection*{Service to the Profession}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item Manuscript Reviewer, \emph{Journal of Politics and Policy}, 2022--present
  \item Manuscript Reviewer, \emph{Journal of Public and Nonprofit Affairs}, 2019--present
  \item Manuscript Reviewer, \emph{Journal of Political Science Education}, 2018--present
  \item Panel Chair, Environment and Public Policy, Midwest Political Science Association Annual Meeting, 2018
  \item Panel Chair, Flirting with Disaster: Politics, the Environment \& Public Policy, Midwest Political Science Association Annual Meeting, 2017
  \item Round Table Participant, Teaching: Graduate Education, Midwest Political Science Association Annual Meeting, 2017
  \item Deil Wright Best Paper in Federalism Award Reviewer, American Political Science Association Annual Meeting, 2016
  \item Student Affairs Committee Member, International Society for Social and Natural Resources, 2013--2014
  \item Discussant, Federalism and Intergovernmental Relations Panel, Southern Political Science Association Annual Meeting, 2013
  \item Panelist, Assessment and Teaching Political Science Round Table, Southern Political Science Association Annual Meeting, 2012
\end{itemize}


\section*{Professional Memberships}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item American Political Science Association
  \item American Society for Public Administration
  \item International Society for Social and Natural Resources
  \item Pi Sigma Alpha National Political Science Honor Society
  \item Pi Alpha Alpha National Public Affairs and Administration Honor Society
\end{itemize}

	
% Footer
\vspace{.5in}
%\vspace{5cm}
\begin{center}
  \begin{small}
    Last updated: \today
      \end{small}
\end{center}

\end{document}	
	











