 % David P. Adams - Curriculum Vitae
%
% Copyright (C) 2024 David P. Adams dpadams@fullerton.edu
%
% Adapted from http://jblevins.org/cv.tex

\documentclass[12pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\frenchspacing
\clubpenalty=500000
\widowpenalty=500000
% Set your name here
\def\name{David P. Adams}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {public policy, public administration, environmental policy, federalism, collaborative governance, social networks, American political institutions, public service ethics, political science pedagogy},
  pdftitle = {\name: David P. Adams - Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}


% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bf\mdseries\Large}
\subsectionfont{\rmfamily\bf\mdseries\itshape\large}
\subsubsectionfont{\rmfamily\bf\mdseries\itshape\normalsize}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\begin{document}
	
% Place name at left
%{\huge \name}
	
% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}
\smallskip
\centerline{\small{\textsc{curriculum vitae}}}

\bigskip

% Contact Information
\noindent

\begin{minipage}[t]{0.55\textwidth}
    Division of Politics, Administration, and Justice \\
    California State University, Fullerton \\
    800 North State College Boulevard  \\
    Fullerton, California 92834
  \end{minipage}
  \hspace{1in}
  \begin{minipage}[t]{0.375\textwidth}
    Office: \hspace{5.1em}(657) 278-4770 \\
    Cell: \hspace{5.6em} (949) 659-3621 \\
    Website: \hspace{6.25em}\href{https://dadams.io}{dadams.io} \\
    Email: \hspace{1.25em}\href{mailto:dpadams@fullerton.edu}{dpadams@fullerton.edu}
  \end{minipage}


  \section*{Education}

  \begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item Ph.D., Public Policy and Public Administration, Auburn University, May 2016. \vspace{0.2cm}
      % Received May 22, 2016
  \item Master of Public Administration, Auburn University, May 2010. \vspace{0.2cm}
    % Received May 14, 2010
  \item B.S., Political Science and Government, Kennesaw State University, May 2008.
    % Received May 14, 2008
  \end{itemize}
  
  \section*{Academic Appointments}

  \begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
      \item Associate Professor of Public Administration, Division of Politics, Administration, and Justice, California State University, Fullerton, 2022--Present. \vspace{0.2cm}
      \item Assistant Professor of Public Administration, Division of Politics, Administration, and Justice, California State University, Fullerton,  2016--2022.\vspace{0.2cm}
      \item Adjunct Professor, Department of Political Science, Auburn University, Summer 2016.
  \end{itemize}

\section*{Research}

\subsection*{Publications}

\subsubsection*{Peer-Reviewed Journal Articles}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt



	\item \href{https://escholarship.org/uc/item/2mz2n6qk}{``Affluence, Risk, and Community Engagement: The Case of Ascon and Huntington Beach.''} with Meriem Doucette and Justin Tucker; \emph{California Journal of Politics and Policy}, 2019, Volume 11(3).
	
	\item \href{https://doi.org/10.1111/polp.12401}{``Crude Contempt: Examining Local Pushback to Oil and Gas Development in California''} with Zachary Mahfuza and Jonathan Fisk; \emph{Journal of Politics and Policy}, 2021, Volume 49(2).

	
\end{itemize}

\subsubsection*{Books}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Adams, David, P., Jonathan M. Fisk, and John Morris. \emph{Navigating Water Quality Outcomes in American Watersheds}. Under Contract with Cambridge University Press: New York, N.Y.
\end{itemize}

\subsubsection*{Edited Textbooks}
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item Doucette, Meriem, and David P. Adams, eds. 2019. \emph{Ethics in Public Administration: Ethics, Corruption, and Public Policy}. Cognella: San Diego, Calif. 
	\end{itemize}

\subsubsection*{Textbook Chapters}
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item Adams, David P. 2019 ``Minnesota Environmental Policy'' in \textit{Minnesota Government and Politics}, edited by Cottrill, James B. and Shawn E. Schooley, Steven C. Wagner, and Shoua S. Yang. Great River Learning Publishers: Dubuquo, Iowa. 
	\end{itemize}

\subsection*{Manuscripts Under Review}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	\item Nahar, Nurun, David P. Adams, Jonathan M. Fisk, Adam F. Mayer, and John C. Morris. ``Inspector-Level Bureaucracy: Drilling into Discretion in a State Natural Resource Agency.'' Under review at \emph{American Review of Public Administration}.
	\item Amin, Alisha, David P. Adams, Jonathan M. Fisk, and Adam F. Mayer. ``Plugged In? Assessing the Distribution of Orphaned Wells.'' Under review at \emph{Journal of Environmental Policy and Planning}.
  \item McKnight, Steve, David P. Adams, and Jonathan M. Fisk. ``Does Disclosure Matter? Coupling Information to Performance in Texas.'' Under review at \emph{Public Administration Review}.
\end{itemize}

% \subsection*{Working Papers}
% \begin{itemize}% \leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
% \item 
% \end{itemize}

\subsection*{Refereed Presentations}
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt

    \item ``Inspector-Level Bureaucracy: Drilling into Discretion in a State Natural Resource Agency,'' paper co-authored with Nurun Nahar, Jonathan M. Fisk, Adam F. Mayer, and John C. Morris. Presented at the national conference of the American Society for Public Administration, Minneapolis, Minn., March 2024.

    \item ``Does Disclosure Matter? Coupling Information to Performance in Texas,'' paper co-authored with Jonathan M. Fisk and Steve McKnight. Presented at the national conference of the American Society for Public Administration, Minneapolis, Minn., March 2024.
    
    \item ``Plugged In? Assessing the Distribution of Orphaned Wells,'' paper co-authored with Alisha Amin, Jonathan M. Fisk, and Adam F. Mayer. Presented at the annual conference of the Midwest Political Science Association, Chicago, Ill., March 2024.
		
		\item ``Head for The Hills: An Environmental Justice Inquiry of Spills within Colorado's Oil and Gas Industry," paper co-authored with Zachary Mahafza, Jonathan M. Fisk, and Hanna Krawczyk. Presented at the virtual national conference of the American Public Administration Society, April 2021. 
		
		\item ``American Indian Youth and Substance Use: Multilevel Analysis of School Related Factors,'' paper co-authored with Veronica Herrera and Lidia E. Nu\~no and chosen through a competitive selection process for presentation as part of the special event ``Adolescence in the Context of Domestic and Global Diversity'' at the Society of Research on Adolescence (SRA) Biennial Meeting, San Diego, Calif., March 2020. 
		
		\item ``Energy Efficiency Retrofits in Underserved Communities,'' paper presented at the International Symposium on Society and Natural Resource Management, Oshkosh, Wisc., June 2019.
		
		\item ``Affluence, Risk, and Community Engagement: The Case of Ascon and Huntington Beach,'' paper presented at the Midwest Political Science Association Annual Meeting, Chicago, Ill., April 2018.
		
		\item ``Central Network Importance for Collaborative Environmental Management,'' paper presented at the American Political Science Association Annual Meeting, San Francisco, Calif., September 2015.
		
		\item ``Central Network Importance for Water Quality,'' paper presented at the International Symposium on Society and Resource Management Annual Meeting, Charleston, S.C., June 2015.
		
		\item ``Environmental Outcomes of Local Watershed Information Networks,'' paper presented at the Midwest Political Science Association Annual Meeting, Chicago, Ill., April 2014.
		
		\item ``Outstanding Programs and Potential Policy Diffusion Across the States,'' paper co-authored Cynthia Bowling and Kisha Hardwick presented at the Southern Political Science Association Annual Meeting, New Orleans, La., January 2014. 
		
		\item ``Broadband Connections and Voter Turnout,'' paper co-authored John Koehler presented at the Southern Political Science Association Annual Meeting, Orlando, Fla., January 2013.
		
		\item ``Enhancing Graduate Student Learning through Course Coordination and Integrated Assignments,'' paper co-authored with Kathleen Hale and Mitchell Brown presented at The Teaching and Learning Conference of the American Political Science Association Annual Meeting, Washington, D.C., May 2012.
		
		\item ``Enhancing Student Learning through Multi-Course Coordination and Learning Module Integration,'' paper co-authored with Kathleen Hale and Mitchell Brown presented at the Southern Political Science Association Annual Meeting, New Orleans, La., January 2012.
		
		\item ``Constructing and Combating an Environmental Problem: Nonpoint Source Pollution in the Wolf Bay Watershed,'' poster presented at the Auburn University Department of Agriculture Economics and Rural Sociology Mobile Bay Watershed Project Annual Meeting, Auburn, Ala., May 2010.
	\end{itemize}
	


\section*{Dissertation}
    \begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
        \item \emph{Dissertation:} ``The Environmental Outcomes of Collaborative Natural Resource Institutions.'' 
        \item \emph{Committee:} Kathleen Hale (Chair), Mitchell Brown (Co-chair),
        Gerry Gryski, \\Linda Dennard, and Elise Irwin.
        \item \emph{Award:} Auburn University Graduate School's Distinguished Dissertation Award
    \end{itemize}
		
\section*{Teaching Experience}
\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	
\subsection*{California State University, Fullerton}
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item Collaborative Governance, POSC 588
		\item Politics and Policy Making in America, POSC 315
		\item Introduction to Public Administration, POSC 320
		\item Foundations of Public Administration, POSC 509
		\item Capstone: Public Administration Theory, POSC 521
	\end{itemize}
	
\subsection*{Auburn University}
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item State and Local Government
		\item Introduction to Public Administration
        \item Research Methods I
        \item Introduction to Political Theory
        \item American Government
        \item Policy Process	
	\end{itemize}
	
\section*{Invited Lectures}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	\item ``Collaborative Water Policy in an Era of Fragmented Federalism,'' Seminar in Environmental Policy, Auburn University--Montgomery, Public Administration 6170, Dr. Linda Dennard.
	
	\item ``Federalism, Environmental Policy, and 21st Century Challenges,'' Guest Lecture for American Government in a Multicultural World, Auburn University, Political Science 1090, Avery Livingston, Esq. 
	
\end{itemize}

\section*{Grants, Honors, and Awards}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
  \item California State University, Fullerton Award for Outstanding Service, 2023.
	\item California State University, Fullerton Office of Research and Sponsored Projects Summer Grant for \$5,000, 2021.
	\item California State University, Fullerton Faculty Advisor of Distinction Award, 2018.
	\item Auburn University Graduate School Distinguished Dissertation Award, 2016.
	\item Auburn University Department of Political Science PhD Student of the Year Award, 2016.
	\item Auburn University College of Liberal Arts GTA Teaching Award, 2016.
	\item SPSA Prestage-Cook Travel Award, 2014.
	\item Omicron Delta Kappa Honor Society, 2013.
	\item Delta Epsilon Iota Honor Society, 2013.
	\item John and Elizabeth Morris Fund for Excellence Travel Grant, 2012.
	\item Auburn University College of Liberal Arts Dissertation Research and Travel Grant, 2012.
	\item Pi Sigma Alpha Honor Society, 2011.
	\item Golden Key International Honour Society, 2010.
	\item Best Performance Award for MPA Comprehensive Exam, 2010.
	\item Pi Alpha Alpha Honor Society, 2009.
\end{itemize}

\section*{Professional Development}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item NASPAA Accreditation Institute, 2017, 2024
    \item Data Analysis with Python Certification, FreeCodeCamp, 2021
    \item Interuniversity Consortium for Political and Social Research (ICPSR) Summer Program in Quantitative Methods of Social Research, University of Michigan, 2012. 
    \item Teaching and Learning Conference of the American Political Science Association, Washington, D.C., 2012.
\end{itemize}

\section*{Service}

\subsubsection*{Service to the Public Administration Program at California State University, Fullerton}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item MPA Program Faculty Advisor, 2024--present.
    \item MPA Program Director, 2023--present.
    \item MPA Program Admissions Coordinator, 2023--present.
    \item Pi Alpha Alpha Honor Society Faculty Advisor, 2023--present.
    \item MPA Program Awards Committee, 2018--present
    \item MPA Program Assessment Coordinator, 2017--present.
    \item MPA Program NASPAA Accreditation Liaison, 2017--present.
    \item MPA Program Curriculum Committee, 2020--2022.
\end{itemize}

\subsubsection*{Service to the Division of Politics, Administration, and Justice at California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Division Personnel Review Committee, 2023--present.
    \item Executive Committee, 2018--2022, 2023--present.
    \item Public Administration Faculty Search Committee, 2023--2024
    \item Part-Time Division Personnel Review Committee, 2022--2023. 
    \item Curriculum Committee, 2020--2022.
    \item Graduation Commencement Committee member, 2017 and 2018. 
\end{itemize}

\subsubsection*{Service to the College of Humanities and Social Sciences at California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Faculty Research and Grants Committee, 2023--present.
\end{itemize}

\subsubsection*{Service to the University at California State University, Fullerton}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item Assessment \& Educational Effectiveness Committee, 2024--present.
    \item Faculty Advisor, Tau Kappa Epsilon International Fraternity, 2017--present
    \item Member, G.E. Assessment Faculty Learning Community, 2019--2021.
    \item Faculty Advisor, United Nations Association - USA; Generation United Nations, 2017--2019.
\end{itemize}

\subsubsection*{Service to the Profession}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	\item Manuscript Reviewer, Journal of Public and Nonprofit Affairs, 2019--present.
	\item Manuscript Reviewer, Journal of Political Science Education, 2018--present.
	\item Panel Chair, Environment and Public Policy, Annual Meeting of the Midwest Political Science Association, 2018.
	\item Panel Chair, Flirting with Disaster- Politics, the Environment \& Public Policy, Annual Meeting of the Midwest Political Science Association, 2017. 
	\item Round Table Participant, Teaching: Graduate Education, Annual Meeting of the Midwest Political Science Association, 2017.
	\item Deil Wright Best Paper in Federalism Award Reviewer, Annual Meeting of the American Political Science Association, 2016.
	\item Student Affairs Committee member, International Society for Social and Natural Resources, 2013--2014.
	\item Discussant, Federalism and Intergovernmental Relations Panel, Annual Meeting of the Southern Political Science Association, 2013.
	\item Panelist, Assessment and Teaching Political Science Round Table, Annual Meeting of the Southern Political Science Association, 2012.
\end{itemize}

\section*{Professional Affiliations}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	\item American Political Science Association
	\item American Society for Public Administration
	\item International Society for Social and Natural Resources
	\item Western Political Science Association
\end{itemize}

	
% Footer
\vspace{2in}
%\vspace{5cm}
\begin{center}
  \begin{small}
    Last updated: \today
      \end{small}
\end{center}

\end{document}	
	











