 % David P. Adams - Curriculum Vitae
%
% Copyright (C) 2018 David P. Adams dpadams@fullerton.edu
%
% Adapted from http://jblevins.org/cv.tex

\documentclass[11pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\frenchspacing
\clubpenalty=500000
\widowpenalty=500000
% Set your name here
\def\name{David P. Adams}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {public policy, public administration, environmental policy, methodology, american government},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}


% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\begin{document}
	
% Place name at left
%{\huge \name}
	
% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}
\smallskip
%\centerline{\small{\textsc{curriculum vitae}}}

\bigskip

\begin{minipage}[t]{0.495\textwidth}
  Division of Politics, Administration, and Justice \\
  California State University, Fullerton \\
  800 North State College Boulevard  \\
  Fullerton, California 92834
\end{minipage}
\hspace{1.25in}
\begin{minipage}[t]{0.495\textwidth}
  Office: (657) 278-4770 \\
  Cell \hspace{.75em} (334) 750-2639 \\
  Fax: \hspace{1em}(657) 278-3524 \\
  Email: \href{mailto:dpadams@fullerton.edu}{\texttt{dpadams@fullerton.edu}}
\end{minipage}

\section*{Academic Appointments}

	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item Assistant Professor of Public Administration, Division of Politics, Administration, and Justice, California State University, Fullerton, Fall 2016--Present.
		\item Adjunct Professor, Department of Political Science, Auburn University, Summer 2016.
	\end{itemize}

\section*{Education}

\begin{itemize}
  \item Ph.D., Public Policy and Public Administration, Auburn University, May 2016.
  	% Received May 22, 2016
    \begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
    \item \emph{Dissertation:} ``The Environmental Outcomes of Collaborative Natural Resource Institutions.'' 
    \item \emph{Committee:} Kathleen Hale (Chair), Mitchell Brown (Co-chair),
	Gerry Gryski, \\Linda Dennard, and Elise Irwin.
	\item \emph{Award:} Auburn University Graduate School's Distinguished Dissertation Award
    \end{itemize}
  \item Master of Public Administration, Auburn University, May 2010.
    % Received May 14, 2010
  \item B.S., Political Science and Government, Kennesaw State University, May 2008.
    % Received May 14, 2008
\end{itemize}

\section*{Fields of Research Interest}

Public Policy, Public Administration, Environmental Policy, Federalism and Intergovernmental Relations, Collaborative Governance, Social Networks, American Political Institutions, Public Service Ethics, Political Science Methodology, Political Science Pedagogy

\section*{Research}

\subsection*{Manuscripts Under Review}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
%	\item ``Central Position of Regional Nonprofits and Environmental Outcomes in the United States.''	
%	\item ``Improving Graduate Student Learning through Sequenced Courses and Integrated Assignments'' (with Mitchell Brown, Kathleen Hale, and John Hall).
	\item ``Affluence, Risk, and Community Engagement: The Case of Ascon and Huntington Beach.'' (with Meriem Doucette and Justin Tucker; Under review at the California Journal of Politics and Policy).
\end{itemize}

\subsection*{Working Papers}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt

\item Watershed Governance: Internal and External Boundaries of Complex Institutional Arrangements
\item Gendered Bias and Blinded Hiring in the Public Sector (with Meriem Doucette and Nicole Akridge).
\item Risk and Protective Factors Associated with Substance Use in Native American Youth (with Lidia Nu\~no and Veronica Herrera). 
\item Experiential Learning in Public Administration: City Manager Fellowships and Internships (with Meriem Doucette and Stephen Coffee).
\item Motivations for Performing Energy Efficient Retrofits in California Residential Homes (with John Shipman)
\item Measuring Water Quality Outcomes from Watershed Partnership Activity in the United States.
\item Outcome-based Typologies for Watershed Governance Organizations.
\end{itemize}

\subsection*{Refereed Presentations}
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item ``Affluence, Risk, and Community Engagement: The Case of Ascon and Huntington Beach,'' paper presented at the Midwest Political Science Association Annual Meeting, Chicago, Ill., April 2018.
		
		\item ``Central Network Importance for Collaborative Environmental Management,'' paper presented at the American Political Science Association Annual Meeting, San Francisco, Calif., September 2015.
		
		\item ``Central Network Importance for Water Quality,'' paper presented at the International Symposium on Society and Resource Management Annual Meeting, Charleston, S.C., June 2015.
		
		\item ``Environmental Outcomes of Local Watershed Information Networks,'' paper presented at the Midwest Political Science Association Annual Meeting, Chicago, Ill., April 2014.
		
		\item ``Outstanding Programs and Potential Policy Diffusion Across the States,'' paper co-authored Cynthia Bowling and Kisha Hardwick presented at the Southern Political Science Association Annual Meeting, New Orleans, La., January 2014. 
		
		\item ``Broadband Connections and Voter Turnout,'' paper co-authored John Koehler presented at the Southern Political Science Association Annual Meeting, Orlando, Fla., January 2013.
		
		\item ``Enhancing Graduate Student Learning through Course Coordination and Integrated Assignments,'' paper co-authored with Kathleen Hale and Mitchell Brown presented at The Teaching and Learning Conference of the American Political Science Association Annual Meeting, Washington, D.C., May 2012.
		
		\item ``Enhancing Student Learning through Multi-Course Coordination and Learning Module Integration,'' paper co-authored with Kathleen Hale and Mitchell Brown presented at the Southern Political Science Association Annual Meeting, New Orleans, La., January 2012.
		
		\item ``Constructing and Combating an Environmental Problem: Nonpoint Source Pollution in the Wolf Bay Watershed,'' poster presented at the Auburn University Department of Agriculture Economics and Rural Sociology Mobile Bay Watershed Project Annual Meeting, Auburn, Ala., May 2010.
	\end{itemize}
	
\section*{Textbooks}
	\begin{itemize}
		\item Doucette, Meriem, and David P. Adams. 2019. \emph{Ethics in Public Administration: Ethics, Corruption, and Public Policy}. Cognella: San Diego, Calif. 
	\end{itemize}
		
\section*{Experience}

\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	
\item California State University, Fullerton, Division of Politics, Administration \& Justice, Assistant Professor.
	\begin{itemize}
		\item Collaborative Governance, POSC 588
		\item Politics and Policy Making in America, POSC 315
		\item Foundations of Public Administration, POSC 509
	\end{itemize}
	
\item Auburn University, Department of Political Science, Adjunct Instructor, Undergraduate Courses, Summer 2016.
	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item State and Local Government, Summer 2016
	\end{itemize}
	
\item Auburn University, Department of Political Science, Instructor of Record, Undergraduate Courses, Summer 2013--Spring 2016.
  	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
			\begin{multicols}{2}
			\item Intro. to Public Administration, Spring 2016
			\item Research Methods I, Fall 2015      
			\item Intro. to Political Theory, Summer 2015
			\item American Government, Spring 2015
			\item Policy Process, Fall 2014	
			\item Policy Process, Spring 2014
			\item Research Methods I, Fall 2013
			\item Intro. to Political Theory, Summer 2013
		 	\end{multicols}				
	\end{itemize}

\item Auburn University, College of Liberal Arts, Research Assistant for Academic Affairs,
  Spring 2008--Summer 2013.
  	\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
		\item Institutional research for the College, examining instruction and expenditure characteristics for departments within the College, across the University, and at peer institutions.   
		\item Student Learning Outcomes Assessment Coordinator for the College and its departments, including preparing for and guiding the College through the Southern Association of Colleges and Schools reaffirmation process, and working with the University's Office of Institutional Research and Assessment.
	\end{itemize}
\end{itemize}
		

\section*{Additional Education}
\begin{itemize}
\item Interuniversity Consortium for Political and Social Research (ICPSR) Summer Program in Quantitative Methods of Social Research, University of Michigan, 2012. 
%	\begin{itemize}
%		\begin{multicols}{2}
%		\item Regression Analysis II
%		\item Maximum Likelihood Estimation
%		\item Categorical Data Analysis
%		\item Matrix Algebra
%		\end{multicols}
%	\end{itemize}
\end{itemize}

\section*{Invited Lectures}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	\item ``Collaborative Water Policy in an Era of Fragmented Federalism,'' Seminar in Environmental Policy, Auburn University--Montgomery, Public Administration 6170, Dr. Linda Dennard.
	
	\item ``Federalism, Environmental Policy, and 21st Century Challenges,'' Guest Lecture for American Government in a Multicultural World, Auburn University, Political Science 1090, Avery Livingston, Esq. 
	
\end{itemize}

\section*{Grants, Honors, and Awards}
\begin{itemize}
	\item California State University, Fullerton Faculty Advisor of Distinction Award, 2018
	\item Auburn University Graduate School Distinguished Dissertation Award, 2016
	\item Auburn University Department of Political Science PhD Student of the Year Award, 2016
	\item Auburn University College of Liberal Arts GTA Teaching Award, 2016
	\item SPSA Prestage-Cook Travel Award, 2014
	\item Omicron Delta Kappa Honor Society, 2013
	\item Delta Epsilon Iota Honor Society, 2013
	\item John and Elizabeth Morris Fund for Excellence Travel Grant, 2012
	\item Auburn University College of Liberal Arts Dissertation Research and Travel Grant, 2012
	\item Pi Sigma Alpha Honor Society, 2011
	\item Golden Key International Honour Society, 2010
	\item Best Performance Award for MPA Comprehensive Exam, 2010
	\item Pi Alpha Alpha Honor Society, 2009
\end{itemize}


\section*{Professional Service}
\begin{itemize}\leftmargin=2pt\labelindent=5pt\itemindent=-15pt
	\item Panel Chair, Environment and Public Policy, Annual Meeting of the Midwest Political Science Association, 2018.
	\item Panel Chair, Flirting with Disaster- Politics, the Environment \& Public Policy, Annual Meeting of the Midwest Political Science Association, 2017. 
	\item Round Table Participant, Teaching: Graduate Education, Annual Meeting of the Midwest Political Science Association, 2017.
	\item Deil Wright Best Paper in Federalism Award Reviewer, Annual Meeting of the American Political Science Association, 2016.
	\item Student Affairs Committee member, International Society for Social and Natural Resources, 2013--2014.
	\item Discussant, Federalism and Intergovernmental Relations Panel, Annual Meeting of the Southern Political Science Association, 2013.
	\item Panelist, Assessment and Teaching Political Science Round Table, Annual Meeting of the Southern Political Science Association, 2012.
\end{itemize}

\section*{Division Service at California State University, Fullerton}
	\begin{itemize}
		\item Division of Politics, Administration, and Justice Executive Committee, 2018--present. 
		\item Public Administration Assessment and Accreditation Coordinator, 2017--present.
		\item NASPAA Accreditation Liaison, 2017--present.
		\item Graduation Commencement Committee member, 2017 and 2018.
		\item Paper Reader for Irving Stone Prize, MPA Program, 2017.
		\item Evaluator for Alan Saltzstein Excellence Scholarship, MPA Program, 2017. 
	\end{itemize}

\section*{University Service at California State University, Fullerton}
	\begin{itemize}
		\item Faculty Advisor, Tau Kappa Epsilon International Fraternity, 2017--present
		\item Faculty Advisor, United Nations Association - USA; Generation United Nations, 2017--present.
	\end{itemize}
	
\section*{University Service at Auburn University}
\begin{itemize}
	\item University Assessment Specialist Search Committee member, 2015--2016.
	\item University Scholarship Committee member, 2012--2016.
	\item College of Liberal Arts Assessment Council member, 2009--2014.
	\item University Ombudsperson Search Committee member, 2014.  
	\item Student Government Association, Senator At-large for the Graduate School, 2013--2014.
	\item Student Government Association, Budget and Finance Committee member, 2013--2014.
	\item College of Liberal Arts Civic Engagement Committee member, 2011--2013.
	\item College of Liberal Arts Imagining America Program Committee member, 2011--2013.
\end{itemize}

\section*{Departmental Service at Auburn University}
	\begin{itemize}
		\item \LaTeX~Brown-Bag Seminar series for faculty and graduate students, Spring 2016.
		\item Lead Graduate Teaching Assistant, Department of Political Science, 2015--2016.
		\item Stata Brown-Bag Seminar series for faculty and graduate students, Spring 2015.
		\item Graduate Student Council, Senator, Department of Political Science, 2012--2014.
		\item President, Pi Alpha Alpha Public Administration Honor Society, 2009--2013.
	\end{itemize}

\section*{Professional Affiliations}
\begin{itemize}
	\item American Political Science Association
	\item American Society for Public Administration
	\item International Society for Social and Natural Resources
	\item Midwest Political Science Association
	\item Western Political Science Association
\end{itemize}

%\newpage

%\section*{Professional References}
%	\begin{itemize}
%		\item Kathleen Hale, JD PhD\\
%			Associate Professor, Department of Political Science\\
%			8030 Haley Center\\
%			Auburn University, Ala. 36849 \\
%			(334) 844-5370 \\
%			\href{mailto:halekat@auburn.edu}{\texttt{halekat@auburn.edu}}
%		
%		\item M. Mitchell Brown, PhD\\
%			Associate Professor, Department of Political Science\\
%			7080 Haley Center\\
%			Auburn University, Ala. 36849\\
%			(334) 844-9644 \\
%			\href{mailto:brown11@auburn.edu}{\texttt{brown11@auburn.edu}}
%		
%			
%		\item Constance Relihan, PhD\\
%			Professor of English and Associate Provost for Undergraduate Studies\\
%			208 Samford Hall\\
%			Auburn University, Ala. 36849\\
%			(334) 844-5771\\
%			\href{mailto:relihco@auburn.edu}{\texttt{relihco@auburn.edu}}
%	\end{itemize}

	
% Footer
\bigskip
%\vspace{5cm}
\begin{center}
  \begin{small}
    Last updated: October 2018
      \end{small}
\end{center}

\end{document}	
	











