% David P. Adams - 2-Page CV for Mellon New Directions
% Compact, public-facing emphasis; preserves your typography/accessibility

\DocumentMetadata{
  pdfstandard=UA-2,
  pdfversion=2.0,
  lang=en-US
}
\documentclass[12pt,letterpaper]{article}

\usepackage[american]{babel}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{sectsty}
\frenchspacing
\clubpenalty=500000
\widowpenalty=500000

\def\name{David P. Adams}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  pdfauthor={\name},
  pdfkeywords={public administration, public policy, environmental governance, spatial equity, collaborative governance, GIS},
  pdftitle={\name: Curriculum Vitae (2 pages)},
  pdfsubject={Curriculum Vitae},
  pdfpagemode=UseNone
}

% Slightly tighter body box to reliably fit in 2 pages
\geometry{
  body={6.5in, 9.4in},
  left=1.0in,
  top=0.7in
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

\usepackage{fontspec}
\setmainfont{Fira Sans}[
  UprightFont = *-Regular,
  BoldFont    = *-Bold,
  ItalicFont  = *-Italic,
  BoldItalicFont = *-BoldItalic
]

\sectionfont{\sffamily\bfseries\Large}
\subsectionfont{\sffamily\bfseries\itshape\large}
\subsubsectionfont{\sffamily\bfseries\itshape\normalsize}

\setlength\parindent{0pt}

% Compact list environments
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.2em}
    \setlength{\itemsep}{0.15em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.15em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.15em}

% Accessibility tagging if available
\IfFileExists{tagpdf-base.sty}{
  \usepackage{tagpdf}
  \tagpdfsetup{activate-all=true, interwordspace=true}
}{
  \newcommand\tagpdfsetup[1]{}
}

\begin{document}

\centerline{\huge \bf \name}
\smallskip
\centerline{\small{\textsc{curriculum vitae (two pages)}}}
\bigskip

\begin{minipage}[t]{0.57\textwidth}
Division of Politics, Administration, and Justice \\
California State University, Fullerton \\
800 North State College Boulevard \\
Fullerton, California 92834
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth}
\begin{tabular}{@{}ll}
Office: & (657) 278-4770 \\
Cell: & (949) 659-3621 \\
Web: & \href{https://dadams.io}{dadams.io} \\
Email: & \href{mailto:dpadams@fullerton.edu}{dpadams@fullerton.edu}
\end{tabular}
\end{minipage}

\vspace{0.6em}

\section*{Education \& Academic Appointments}
\textbf{Education}\\
Ph.D., Public Policy and Public Administration, Auburn University, 2016 \\
M.P.A., Auburn University, 2010 \quad|\quad B.S., Political Science, Kennesaw State University, 2008

\vspace{0.3em}
\textbf{Appointments}\\
Associate Chair \& MPA Director, CSUF, 2024--present \\
Associate Professor (tenured), CSUF, 2022--present \\
Assistant Professor, CSUF, 2016--2022 \\
Adjunct Professor, Auburn University, Summer 2016

\section*{Research Focus}
Environmental governance; administrative capacity \& collaborative networks; \textbf{spatial equity} in policy design and outcomes; technology, data, and institutions. Current work advances \textbf{GIS- and PostGIS-based} spatial analysis to evaluate distributional impacts and administrative performance in climate investments, oil \& gas, and public safety technologies.

\section*{Selected Peer-Reviewed Publications (2019--2025)}
\begin{itemize}
  \item Nahar, N., J. C. Morris, J. A. Aistrup, D. P. Adams, J. M. Fisk, \& A. P. Mayer (2025). \emph{Inspector-Level Bureaucracy: Drilling into Discretion in a State Natural Resource Agency}. \emph{Environmental Policy and Governance}. \href{https://doi.org/10.1002/eet.70038}{doi:10.1002/eet.70038}
  \item Adams, D. P. (2025). \emph{The Code Is the Policy: Blockchain Governance and the Authoritarian Pursuit of Administrative Efficiency}. \emph{Administrative Theory \& Praxis}.
  \item Adams, D. P., J. M. Fisk, \& A. P. Mayer (2025). Administrative Resilience Under Pressure. \emph{Administrative Theory \& Praxis}, 1--7. \href{https://doi.org/10.1080/10841806.2025.2537600}{doi}
  \item McKnight, S., D. P. Adams, \& J. M. Fisk (2025). Does Disclosure Matter? \emph{Policy Studies Journal}, 1--12. \href{https://doi.org/10.1111/psj.70064}{doi}
  \item Amin, A., D. P. Adams, J. M. Fisk, \& A. P. Mayer (2025). Plugged In? Orphaned Wells. \emph{Journal of Environmental Policy \& Planning}, 1--14. \href{https://doi.org/10.1080/1523908X.2025.2480289}{doi}
  \item Arthur, P., D. P. Adams, J. M. Fisk, M. G. Jarvis, \& C. A. Simon (forthcoming). Multi-Agency Collaboration in California's Climate Investments (2015--2024). \emph{Public Organization Review}. \href{https://doi.org/10.1007/s11115-025-00586-3}{doi}
  \item Adams, D. P., M. Doucette, \& J. Tucker (2019). Affluence, Risk, and Community Engagement. \emph{California Journal of Politics \& Policy} 11(3), 1--19. \href{https://escholarship.org/uc/item/2mz2n6qk}{open}
\end{itemize}

\subsection*{Books}
\begin{itemize}
  \item Adams, D. P., J. M. Fisk, \& J. Morris. \emph{Navigating Water Quality Outcomes in American Watersheds}. Forthcoming, Cambridge University Press.
\end{itemize}

\subsection*{Under Review / In Revision (Selected)}
\begin{itemize}
  \item Nahar, N., D. P. Adams, J. M. Fisk, A. F. Mayer, \& J. C. Morris. Inspector-Level Bureaucracy: Discretion in a State Natural Resource Agency. (revise \& resubmit)
  \item Reill, K., \& D. P. Adams. Equity, Engagement, Ethics, and Empathy: City Manager Vignette Study. (under review)
\end{itemize}

\section*{External Funding, Honors, \& Awards (Selected)}
\begin{itemize}
  \item RSCA Intramural Grant, California State University, Fullerton, \$15,000 (2025--2026)
  \item H\&SS Dean's Research Award for Associate Professors, \$2,500 (Spring 2025)
  \item CSUF Award for Outstanding Service (2023)
  \item ORSP Summer Grant, CSUF, \$5,000 (2021)
  \item Auburn Graduate School Distinguished Dissertation Award (2016)
\end{itemize}

\section*{Public-Facing \& Community-Engaged Work (Selected)}
\begin{itemize}
  \item \textbf{Program partnerships:} Co-produce applied analyses with California state agencies and local governments (data pipelines, dashboards, policy briefs) on climate investments, water quality, and energy transition.
  \item \textbf{Open workflows:} Release reproducible notebooks, documentation, and map-centric outputs where agreements allow; mentor practitioner use.
  \item \textbf{MPA Capstone redesign:} Project-based engagements with municipal partners; integrating equity-centered spatial analysis, decision-support tools, and professional deliverables.
\end{itemize}

\section*{Professional \& Academic Service (Recent, Selected)}
\begin{itemize}
  \item Associate Chair \& MPA Program Director, CSUF (2024--present)
  \item Chair, Division Search Committee (Public Administration) (2025--present)
  \item Chair, Division Personnel Review Committee (2025--present)
  \item NASPAA Accreditation Liaison (2017--present); Assessment Coordinator (2017--present)
  \item Organizer, Environment \& Natural Resources Mini-Conference, ASPA 2026
  \item Manuscript Reviewer: \emph{Administrative Theory \& Praxis}; \emph{Journal of Public and Nonprofit Affairs}; \emph{Journal of Political Science Education}
\end{itemize}

\section*{Selected Teaching}
\textbf{California State University, Fullerton:} POSC 588 (Collaborative Governance); POSC 315 (Intro to Public Policy); POSC 320 (Intro to Public Administration); POSC 509 (Foundations of PA); POSC 521 (Capstone: PA Theory).\\
\textbf{Auburn University:} State \& Local Government; Intro to PA; Research Methods I; Political Theory; American Government; Policy Process.

\section*{Methods \& Technical Competencies}
PostgreSQL/\textbf{PostGIS}; Python (geopandas, rasterio, statsmodels); QGIS; spatial econometrics; remote sensing; network/point-pattern analysis; reproducible research (LaTeX, Git); dashboarding \& web mapping for public audiences.

\section*{Recent Refereed Presentations (Abbrev.)}
\begin{itemize}
  \item Adams et al. Linking Disclosure to Performance (Colorado). ASPA (2025).
  \item Arthur et al. Multi-Agency Collaboration in California CCI (2015--2024). ASPA (2025).
  \item Adams, Fisk, \& Morris. Water Quality Outcomes. ASPA (2024).
  \item Adams et al. Inspector-Level Bureaucracy. ASPA (2024).
  \item Adams, Fisk, \& McKnight. Disclosure \& Performance (Texas). ASPA (2024).
  \item Adams et al. Orphaned Wells Distribution. MPSA (2024).
\end{itemize}

\section*{Professional Memberships}
American Society for Public Administration; International Society for Society \& Natural Resources; Pi Sigma Alpha; Pi Alpha Alpha.

\vfill
\begin{center}
\begin{small}
Last updated: \today
\end{small}
\end{center}

\end{document}
